DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/comparison.tex
comparison revision done

Finally, we compare the effect of co-scheduling memory intensive
synthetic benchmarks on the DNN control loop timing.
Figure~\ref{fig:sys_bench} shows the results. 
experienced a change in their inferencing times, but the increases 
were not as drastic as is seen by the Raspberry Pi 3. in the worst 
case, both the UP Board and TX2 (CPU only and GPU) produced times 
that were over two times as large, whereas the Raspberry Pi 3 output 
times that were around 10 times greater. The Intel UP Board was 
successful in completing inferencing operations in under 50 ms when 
benchmarks were run on a maximum of 2 cores, and the TX2 was 
successful in all experiments irrespective of the computing resources 
utilized. Comparetively, both performed better than the Raspberry Pi 
3 which failed to meet its deadlines when any benchmark was 
introduced. As such, it can be concluded that the Intel UP Board 
would be more capable of running computationally heavy processes 
during autonomous driving, and that the Pi wouldn't be able to do the 
same.

In the comparison of the real-time capabilities of three embedded 
computing platforms, we found that the Raspberry Pi 3 performed the 
worst. When compared to the Intel UP Board and the NVIDIA Tegra TX2, 
control loops on the Pi were shown to take noticably longer to 
complete, regardless of the number of cores utilized or the number of 
neural network models run simultaneoulsy. The difference was even 
more noticeable in the the addition of computationally heavy 
synthetic benchmarks that had a much more dire effect on the Pi. In 
the worst case, an average control loop on the Pi took an abnormally 
long amount of time to finish. Compared to the TX2 with GPU support, 
those times were 34.8X times greater. From this, we find that the UP 
Board and Tegra TX2 are superior platforms for real-time CNN 
operations. However, due to the Pi's ability to satisfy the 50 ms 
WCET in some experiments, we conclude that the Raspberry Pi 3 is 
feasible for autonomous research.

>>>>

Finally, we compare the effect of co-scheduling memory bandwidth
intensive synthetic benchmarks on the DNN control loop timing. 
Figure~\ref{fig:sys_bench} shows the results.
As discussed in 
Section~\ref{sec:eval-memhog}, we observe dramatic execution time
increase, up to 9.4X, in Raspberry Pi 3 as we increase the number of
co-scheduled tasks. We also observe increased control loop execution
timing in Intel Up and TX2, but the degree of the increase is not as
dramatic as the Pi3. Compared to their respective solo timing (i.e.,
the model runs on a single core in isolation), Intel UP suffers up to
2.3X execution time increase; TX2 (CPU) and TX2 (GPU) suffer up to
2.2X and 2.5X increase, respectively. This is somewhat suprising
because Raspberry Pi 3's cores are in-oder architecture based while
the cores in Intel Up and NVIDIA TX2 are out-of-order architecture
based and that the memory intensive tasks on out-of-order cores can
generate more memory traffic. We suspect that this is because the
memory subsystems in the Intel UP and TX2 platforms provide higher
bandwidth and fairness than the memory subsystem of the Pi 3.

Another intersting observation is that TX2 (GPU) also suffers
considerable execution time increase (2.5X) despite the fact that the
co-scheduled synthetic tasks do not utilize the GPU. In other words,
the DNN model has dedicated access to the GPU. This is, however, a
known characteristic of integrated CPU-GPU architectue based
platforms that both CPU and GPU share the same memory
subsystem~\cite{Ali2017}.

%% experienced a change in their inferencing times, but the increases 
%% were not as drastic as is seen by the Raspberry Pi 3. in the worst 
%% case, both the UP Board and TX2 (CPU only and GPU) produced times 
%% that were over two times as large, whereas the Raspberry Pi 3 output 
%% times that were around 10 times greater. The Intel UP Board was 
%% successful in completing inferencing operations in under 50 ms when 
%% benchmarks were run on a maximum of 2 cores, and the TX2 was 
%% successful in all experiments irrespective of the computing resources 
%% utilized. Comparetively, both performed better than the Raspberry Pi 
%% 3 which failed to meet its deadlines when any benchmark was 
%% introduced. As such, it can be concluded that the Intel UP Board 
%% would be more capable of running computationally heavy processes 
%% during autonomous driving, and that the Pi wouldn't be able to do the 
%% same.

In summary, we find that today's embedded computing platforms, even as
inexpensive as a Raspberry Pi 3, are powerful enough to support
vision and end-to-end deep learning based real-time control
applications. Furthermore, availability of CPU cores and GPU on these
platforms allow consolidating mutiple deep neural network based AI
workloads. However, shared resource contention among these diverse
computing resources remain an important issue that must be understood
and controlled especially for safety-critical applications.

%% the comparison of the real-time capabilities of three embedded 
%% computing platforms, we found that the Raspberry Pi 3 performed the 
%% worst. When compared to the Intel UP Board and the NVIDIA Tegra TX2, 
%% control loops on the Pi were shown to take noticably longer to 
%% complete, regardless of the number of cores utilized or the number of 
%% neural network models run simultaneoulsy. The difference was even 
%% more noticeable in the the addition of computationally heavy 
%% synthetic benchmarks that had a much more dire effect on the Pi. In 
%% the worst case, an average control loop on the Pi took an abnormally 
%% long amount of time to finish. Compared to the TX2 with GPU support, 
%% those times were 34.8X times greater. From this, we find that the UP 
%% Board and Tegra TX2 are superior platforms for real-time CNN 
%% operations. However, due to the Pi's ability to satisfy the 50 ms 
%% WCET in some experiments, we conclude that the Raspberry Pi 3 is 
%% feasible for autonomous research.
